\chapter*{Scenario rewriting}

\ifnotes

\fi

\ifcontent

    \QandAbox{1.	Phrase this in "Given, When, Then" format: "Robinson Crusoe" and" Treasure Island" are both classics. If I've got "Robinson Crusoe" in my basket and I go to the checkout, it should recommend "Treasure Island" to me too.}{3}
    
    \QandAbox{2.	Rephrase this scenario so that it doesn't make any reference to GUI elements. Bonus: What could you do that might help you avoid this kind of language? 
    
        \begin{adjustwidth}{1cm}{}
            Given I clicked the buy button for "Robinson Crusoe" at \$12.95\\
            And I'm on the "checkout" page\\
            And postage is \$3.00\\
            When I click "purchase"\\
            Then I should see the text "Thank you! Your purchase is on its way!"\\
            And I should see the text "Total cost: \$15.95"
        \end{adjustwidth}
        }{5}
    

    \QandAbox{3.	Refactor the event (When) so that the context (Given) is in its own step.
    
    \begin{adjustwidth}{1cm}{}
        When Petunia Picky tells that she didn't like the "Early Grey Coffee" we sent her\\
        Then we should skip it in her rotation.
    \end{adjustwidth}
    }{3}
    
    \QandAbox{4.	Refactor the event (When) and create two scenarios. Bonus: why wouldn't you automate both,  if the information you have below is all you've got?
    
    \begin{adjustwidth}{1cm}{}
        Given customers who bought "Sparks" also bought "Speak for Yourself" and "Ellipse"\\
        When Emma Excited buys "Sparks" or "Ellipse"\\
        Then she should be recommended "Speak for Yourself" too.
    \end{adjustwidth}
    }{3}
    
    \QandAbox{5.	Refactor the events (When) so that there's only one of them.
    
    \begin{adjustwidth}{1cm}{}
        Given my basket full of groceries has a total cost of \$23.58\\
        When I say I've finished\\
        And I choose to pay by credit card\\
        And I enter my pin\\
        And the payment is authorized\\
        Then my credit card should be charged \$23.58\\
        And I should get a receipt.
    \end{adjustwidth}
    }{3}
    
    \QandAbox{6.      Refactor the scenario below into the different capabilities of the system. 
  
    \begin{adjustwidth}{1cm}{}
        Given I worked for Acme Ltd. for 4 days at \$300 a day\\
        And I have a 30 day payment schedule\\
        And the date is 22nd October 2014\\
        And 22nd November 2014 is a Saturday\\
        When I invoice Acme by email\\
        Then Acme and I should both get copies of the email\\
        And they should be given a due date of 24th November
    \end{adjustwidth}
    }{4}


\fi