\chapter*{Another Scenario}

\ifnotes

    Learning outcomes:
    
    \begin{itemize}
        \item Explain that for new functionality the failing acceptance test drives the evolution of the production code
        \item Show that a new acceptance tests doesn't always lead to writing new step definitions
        \item New rules need to be transcribed into the top of a feature file
        \item Describe how "listening to your test" can lead to better implementation
    \end{itemize}
    
    They start by FORMULATING a scenario. Then they automate it and see it fail. Then they need to get the code to pass. Ask if anyone wrote a unit test as part of getting to green. Ask them why they did/didn't write a unit test.
    
    Check if they have a step setting up a location for the shouter/listener. Should it be necessary?
    
    Answer: 
    \begin{enumerate}
        \item from a business perspective, NO.
        \item from a technical perspective not if they check the shouter is not the listener before calculating the distance between the shouter and listener.
    \end{enumerate}  
    
    \emph{We should not modify our scenarios/documentation to make the automation easier}
    
\fi 

\ifcontent 
    The product owner has come up with a new rule: "shouters should not hear their own shouts."  
    
    Write a scenario in the feature file that illustrates this rule.
    
    \QandAbox{Does your new scenario pass? What stage of the BDD process are we at now?}{2}
    
    \section*{Get to green}
    
    Depending on what scenario you wrote, you might now need to implement new step definition(s). 
    
    You will certainly need to modify your production code to make your new scenario pass. 
    
    Make sure you don't break any of the existing scenarios.
    
    \QandAbox{How long do you think the cycle of adding a new scenario and getting it to pass usually takes?}{2}
    
    \QandAbox{Does your new scenario have a \texttt{Given} step that specifies someone's location? Do you think that should be necessary?}{2}
\fi