\chapter*{\CUKE{} and non \JAVA{Java}\CSHARP{.NET}\JAVASCRIPT{JavaScript}\RUBY{Ruby}\ interfaces}

\ifnotes

    Learning outcomes:
    
    \begin{itemize}
        \item Explain that Cucumber is only responsible for calling the relevant user defined automation function in response to the business-readable documentation
        \item Describe how automation code can make use of any library available from its runtime environment
    \end{itemize}

    Specifically, Cucumber doesn't know anything about web services or Selenium. But you can write stepdef code that makes use of libraries that do.
\fi 

\ifcontent 
    Some of the scenarios that the business are interested in will be written as end-to-end tests. This means that \CUKE{} may need to interact with web applications or REST services. \CUKE{} doesn't know anything about HTML or web browsers, so what should we do?
    
    All that \CUKE{} can do is run \JAVA{Java}\CSHARP{.NET}\JAVASCRIPT{JavaScript}\RUBY{Ruby}\ step definitions and, luckily, we can use any of the \JAVA{Java}\CSHARP{.NET}\JAVASCRIPT{JavaScript}\RUBY{Ruby}\ libraries that specialise in interacting with diverse interfaces, such as web browsers or REST services. Some of the more popular libraries are:
    
    \begin{itemize}
        \item Selenium Webdriver: to interact with web browsers
        \JAVASCRIPT{\item WebDriverIO (WDIO): to interact with web browsers (using a simpler API than WebDriver native)}
        \JAVASCRIPT{\item Cucumber-Electron: to interact with the DOM in the same Node.js process running the server}   
        \JAVASCRIPT{\item PhantomJS: a headless WebKit scriptable with a JavaScript API}
        \JAVASCRIPT{\item Chakram: Write API tests (synchronous and asynchronous) to verify endpoints work correctly}    
        \RUBY{\item Capybara: to interact with a Ruby web app using a headless browser}
    
        \JAVA{\item Jersey Client: to interact with HTTP/REST APIs}
        \CSHARP{\item RestSharp: to interact with HTTP/REST APIs}
        \RUBY{\item rest-client: to interact with HTTP/REST APIs}
    \end{itemize}
    
    We can interact directly with 
    \JAVA{Java}
    \CSHARP{.NET}
    \JAVASCRIPT{JavaScript}
    \RUBY{Ruby}{}
    production code from our \CUKE{} step definitions. For direct interaction with non 
    \JAVA{Java}
    \CSHARP{.NET}
    \JAVASCRIPT{JavaScript}
    \RUBY{Ruby}{}
    languages there are implementations of Cucumber in several other languages.
\fi