\chapter*{Step definition arguments}

\ifnotes

    Learning outcomes:
    
    \begin{itemize}
        \item  
    \end{itemize}

\fi 

\ifcontent 
    The \JAVA{\texttt{sean\_is\_at} }\CSHARP{\texttt{GivenSeanIsAt}}\JAVASCRIPT{\texttt{\textquotesingle{}Sean is at \LEFTCURLY{}int\RIGHTCURLY{}, \LEFTCURLY{}int\RIGHTCURLY{}\textquotesingle{}}}\RUBY{\texttt{\textquotesingle{}Sean is at \LEFTCURLY{}int\RIGHTCURLY{}, \LEFTCURLY{}int\RIGHTCURLY{}\textquotesingle{}}}\ and \JAVA{\texttt{lucy\_is\_at} }\CSHARP{\texttt{GivenLucyIsAt} }\JAVASCRIPT{\texttt{\textquotesingle{}Lucy is at \LEFTCURLY{}int\RIGHTCURLY{}, \LEFTCURLY{}int\RIGHTCURLY{}\textquotesingle{}}}\RUBY{\texttt{\textquotesingle{}Lucy is at \LEFTCURLY{}int\RIGHTCURLY{}, \LEFTCURLY{}int\RIGHTCURLY{}\textquotesingle{}}}\ step definitions are almost identical except for the person's name. We're already using \texttt{\LEFTCURLY{}int\RIGHTCURLY{}} \emph{output parameters} to extract the coordinates and pass them to the step definition.
    
    Let's replace the person's name in the Cucumber Expressions with another output parameter so that the person's name is also passed to the step definition as an argument.
    
    In the first of the existing step definitions, replace \texttt{Lucy} with \texttt{\LEFTCURLY{}word\RIGHTCURLY{}} to make it an output parameter:
    
    \JAVASCRIPT{\texttt{Given(\textquotesingle\LEFTCURLY{}word\RIGHTCURLY{} is at \LEFTCURLY{}int\RIGHTCURLY{}, \LEFTCURLY{}int\RIGHTCURLY{}\textquotesingle, function (...) \LEFTCURLY{}}}
    \RUBY{\texttt{Given(\textquotesingle\LEFTCURLY{}word\RIGHTCURLY{} is at \LEFTCURLY{}int\RIGHTCURLY{}, \LEFTCURLY{}int\RIGHTCURLY{}\textquotesingle) do |x, y|}}
    
    Now that the cucumber expression has 3 output parameters, the step definition method is going to need an equal number parameters. What type should the new parameter be? What's a good name for it?
    
    Can you see where you can now replace the hard-coded \texttt{"Lucy"} in the body of the step definition method with that parameter?
    
    Run \CUKE{}. Did you get \JAVA{an \texttt{AmbiguousStepDefinitionsException}?}\JAVASCRIPT{a \texttt{Multiple step definitions match} error message?}\RUBY{an \texttt{Ambiguous match} error message?}\CSHARP{a \texttt{BindingException } because of an ambiguous step definition?}\ Why? What do you need to do to fix it?
    
    \answerbox{2}
    
    Run \CUKE{} and check everything is still working as before.
\fi