\chapter*{Introduction}

\TRAINERNOTES{
\section*{Pre-work}

Watch these videos:
\begin{itemize}
    \item \href{https://vimeo.com/15007792} {https://vimeo.com/15007792} (51 min)
    \item \href{https://skillsmatter.com/skillscasts/7361-keynote-kind-of-green} {https://skillsmatter.com/skillscasts/7361-keynote-kind-of-green} (34 min - requires signing up for a free account)
\end{itemize}
}

\section*{Learning outcomes for today}

Take a look at this list below. Highlight the three that are most important important to you.

\begin{itemize}
    \item Draw and annotate the testing pyramid.
    \item Be able to identify reasons why teams end up with a top-heavy test-distribution, and explain the consequences.
    \item Refactor a small part of a system to introduce a port and a concrete adapter.
    \item Implement a test double that mimics an external system or API.
    \item Refactor an existing codebase to use a ports \& adapters / hexagonal architecture
    \item Draw a hexagonal architecture diagram for an example codebase.
    \item List three kinds of feedback that TDD gives you to create a more testable codebase.
    \item Be able to explain how a Ports \& Adapters improves testability in three different ways.
    \item Create a contract test that can drive both a real and test double adapter for an external component, removing the need for an end-to-end test.
    \item Enumerate the pros and cons of three different approaches to test data management.
\end{itemize}

Is there anything else you'd really like to achieve from today?

\answerbox{5}
