\chapter*{What makes for good Gherkin?}

\ifnotes

    Alternative:
    
    \begin{itemize}
        \item Draw a quadrant on the flip chart: Good/Bad vs Scenario1/Scenario2
        \item Ask each table to come up with 1 good thing and 1 bad thing about each of the scenarios \& write them on 4 separate stickies
        \item Put each sticky in the relevant quadrant
        \item When done, your job is to explain why everything "Good" about Scenario 1 is in fact "Bad", and everything "Bad" about Scenario 2 is in fact "Good" 
    \end{itemize}

    Learning outcomes:
    
    \begin{itemize}
        \item Describe why inessential information is harmful
        \item Explain why scenarios should be declarative
        \item Reason why business folk like tabular data
        \item Remember that implicit contexts are best omitted
    \end{itemize}

\fi

\ifcontent

    Read these two scenarios and underline terms that might be part of the team's ubiquitous language (remember that the ubiquitous language should be based on the business domain):

\begin{verbatim}
    Scenario: Dispense $50 cash in multiple denominations
        Given I have $100 in my checking account
        And I have a card with the PIN 5173
        And I push my card into the machine
        And I enter 5173 for my PIN
        And I push the button next to “Withdrawal”
        And I push the button next to “Checking”
        When I push the button next to “$50”
        Then a $20 bill should be ejected by the cash dispenser
        And a $20 bill should be ejected by the cash dispenser
        And a $10 bill should be ejected by the cash dispenser
      
    Scenario: Dispense $50 cash in multiple denominations
        When $50 is dispensed by the ATM
        Then the following bills should be dispensed:
          | count | denomination |
          | 2     | $20          |
          | 1     | $10          |
    
\end{verbatim}

    Discuss with your table group:
    
    \QandAbox{Both these scenarios describe the same behaviour. Which one do you think best expresses the essence of this behaviour from the business perspective?}{1.5}
    
    \QandAbox{What's good about each of them? What's bad about each of them?}{1.5}
    
    \QandAbox{If we were asked to change the system's UI, what effect would that have on these scenarios?
    How might people in different roles see this differently? Why?}{1.5}

\fi
