\chapter*{Before we get started}

While you're waiting for the class to start, read the list of statements below. Try to write T for true and F for false next to each statement.

\begin{enumerate}
\item Testing is something you can only do once developers are done coding.
\item On a software project, it's often the things we didn't know at the beginning that end up making the biggest impact on the project's success or failure.
\item Good developers don't need to test their code.
\item When we want to understand a requirement, getting diverse perspectives can help us to discover unknown unknowns.
\item Gherkin is a syntax for expressing software specifications as plain-text examples.
\item Cucumber is a tool for validating Gherkin specifications.
\item Given / When / Then are the main keywords in Gherkin.
\item Cucumber is a proprietary, closed-source tool with an expensive license.
\item Gherkin was designed to be hard for non-programmers to understand.
\item It's easy to estimate how long it will take to fix a defect.
\item It's easy to keep code clean when you have no tests.
\item Agile iterations / sprints mean a need for more manual regression testing.
\item When a team is using BDD, there is no more need for manual testing.
\item Refactoring is the process of making code complex and difficult to understand.
\item Developers can't test their own code.
\item You can't be truly agile unless you have clean code.
\item You can't have clean code unless you refactor.
\item You can't refactor without good automated tests.
\item Shift-Left is about automated testing and doesn't need the Product Owner's involvement
\item The Product Owner is an essential part of a Scrum team
\item Agile development only really works for web teams
\item Once code is written you should never have to change it
\item If our tests were automated they would get run more often
\item Concrete examples are a good way to get a conversation going about a requirement.
\item Test automation is software development.
\item Most software requirements are well understood before development starts.
\end{enumerate}

Compare your answers with those of a person sitting near you. Did you agree on everything?